---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
body {
  background-color: #121212;
  color: #E0E0E0;
  font-family: "Segoe UI", "Helvetica Neue", sans-serif;
  line-height: 1.6;
  padding: 2em;
}

h2, h3 {
  color: #FF9800;
  border-bottom: 1px solid #333;
  padding-bottom: 5px;
  margin-top: 2em;
}

code {
  background-color: #1E1E1E;
  padding: 2px 5px;
  border-radius: 4px;
  font-family: "Fira Code", monospace;
  color: #00BCD4;
}

pre {
  background-color: #1E1E1E;
  color: #B0BEC5;
  padding: 1em;
  border-radius: 6px;
  overflow-x: auto;
}

table {
  width: 100%;
  border-collapse: collapse;
  margin-top: 1.5em;
}

th, td {
  border: 1px solid #333;
  padding: 0.75em;
  text-align: left;
}

th {
  background-color: #212121;
  color: #FF9800;
}

a {
  color: #64B5F6;
  text-decoration: none;
}

a:hover {
  text-decoration: underline;
}

img {
  max-width: 100%;
  border-radius: 8px;
  margin-top: 1em;
}


```

## How I respond to my Sotify Daily Feeds


This report explores how I respond to different music genres from my **Spotify daily feeds**.

Let's see how genre affects enjoyment and listening patterns.


```{r}
library(tidyverse)


#import data
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vScns1xPkfQxpvfcPueO-Q3zj7TrB9VeXmCvCBz4nuDOTfiqbrub-6mVdHEl3W4rkGooIPgODSCqwqn/pub?output=csv")


print(logged_data)


# Rename columns after importing
latest_data <- logged_data %>%
  rename(
    timestamp = `Timestamp`,
    genre = `What genre is the song?`,
    finished = `Did you finish listening to the entire song?`,
    enjoyment = `How would you rate your enjoyment of this song? (1 to 10)`,
    action_after = `What did you do after listening?`,
    listen_period = `When did you listen to the song?`
  )


# Summary values
enjoyment_mean <- mean(latest_data$enjoyment, na.rm = TRUE)
enjoyment_max <- max(latest_data$enjoyment, na.rm = TRUE)
enjoyment_min <- min(latest_data$enjoyment, na.rm = TRUE)


# Bar chart 1: Number of songs listened to by genre
ggplot(latest_data, aes(x = genre)) +
  geom_bar(fill = "steelblue") +
  labs(title = "Number of Songs Listened to by Genre",
       x = "Genre",
       y = "Count") +
  theme_minimal()


# Bar chart 2: Average enjoyment by genre
latest_data %>%
  group_by(genre) %>%
  summarise(avg_enjoyment = mean(enjoyment, na.rm = TRUE)) %>%
  ggplot(aes(x = genre, y = avg_enjoyment)) +
  geom_col(fill = "darkorange") +
  labs(title = "Average Enjoyment by Genre",
       x = "Genre",
       y = "Average Enjoyment Rating (1–10)") +
  theme_minimal()


# --- Summary of Exploration ---
# Based on the data exploration:
# - The most frequently listened-to genres is Classical.
# - Classical and Jazz had the highest average enjoyment ratings.

```

The **average enjoyment rating** across all songs was **`r round(enjoyment_mean, 1)`**, and the **highest rating** given was **`r enjoyment_max`**.

### Chart 1: Number of Songs Listened to by Genre
This chart shows how often each genre appeared in my Spotify daily feed and was listened to.
Classical songs showed up and were listened to the most, while Hip-hop and Jazz appeared less often.
Pop, R&B, and Rock were more balanced in number.
This gives a quick overview of the genre distribution in the feed, based on what I engaged with.

### Chart 2: Average Enjoyment by Genre
This chart shows how much I enjoyed each genre based on the songs recommended to me.
Jazz and Classical had the highest enjoyment scores, both averaging over 8.
Hip-hop had the lowest score, around 5.
This suggests that while I didn’t choose the songs myself, I had stronger positive reactions to certain genres like Classical and Jazz.





